\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-10-11 papers/methods/paper.tex
More of ricks feedback

To investigate biases in the model in fine detail, we look for systematic bias in $\Omega_m$ in the Flat $\Lambda$CDM cosmology test, and bias in $w$ for the Flat $w$CDM test with strong prior $\Omega_m \sim \mathcal{N}(0.3, 0.01)$. This allows us to investigate biases without the investigative hindrances of non-Gaussian or truncated posterior surfaces. The strong prior on $\Omega_m$ cuts a slice through the traditional `banana' posterior surface in the $w$-$\Omega_m$ plane of Figure \ref{fig:simple_w}. Without making such a slice, the variation in $w$ is larger due to a shift along the degeneracy direction of the `banana'. By focusing the slice at an almost fixed $\Omega_m$, we can see the variation in the mean value of $w$ approximately perpendicular to the lines of degeneracy, instead of along them. The results of the analysis are detailed in Table \ref{tab:simple_model}, and demonstrate the performance of our model in recovering the true cosmological parameters.

@@

>>>>

To investigate biases in the model in fine detail, we look for systematic bias in $\Omega_m$ in the Flat $\Lambda$CDM cosmology test, and bias in $w$ for the Flat $w$CDM test with strong prior $\Omega_m \sim \mathcal{N}(0.3, 0.01)$. This allows us to investigate biases without the investigative hindrances of non-Gaussian or truncated posterior surfaces. The strong prior on $\Omega_m$ cuts a slice through the traditional `banana' posterior surface in the $w$-$\Omega_m$ plane of Figure \ref{fig:simple_w}. Without making such a slice, the variation in $w$ is larger due to a shift along the degeneracy direction of the `banana'. By focusing the slice at an almost fixed $\Omega_m$, we can see the variation in the mean value of $w$ approximately perpendicular to the lines of degeneracy, instead of along them. The results of the analysis are detailed in Table \ref{tab:simple_model}, and demonstrate the performance of our model in recovering the true cosmological parameters. {\green With this simple data, we also correctly recover underlying supernova populations, which can be seen in Figure \ref{fig:simple_w_super}.}

@@

{\green Failure to provide an adequate parametrisation for realistic intrinsic dispersion and the simplification of Malmquist bias to only apparent magnitude also leads to biases in the population parameters. Tests when fixing the population parameters to true does not resolve the cosmological bias observed in the {\celeven} simulations. As the population parameters recovered using the simplistic toy supernova data in the previous section do not exhibit significant bias, future work will focus on intrinsic dispersion and Malmquist bias rather than alternate parametrisations of the underlying supernova population.}
